Soundness Proofs for Iterative Deepening

### 2016-09-01 oopsla-16/proof/proof.tex
oopsla proof: address camreadies
ack pdl consortium in proof

% TODO CAMREADY
% We suspect that DPOR + pure-HB will always eventually find all data races uncovered by MHB.
% for the purpose of iterative deepening, MHB is
% better because it will find the data races much sooner, rather than requiring you
% to explore the maximal state space before the race can be uncovered

@@

%{\em removed for double blind review}
Michael J. ``Sully'' Sullivan, Carlo Angiuli, and Nathaniel Filardo double-checked the proof and provided valuable feedback on notation style and the flow of explanation.
Thanks as well to the anonymous OOPSLA reviewer \#4, whose suggestions helped improve the formality of our definitions.
This work was supported in part by the U.S. Army Research Office under grant number W911NF0910273.

>>>>

@@

%{\em removed for double blind review}
Michael J. ``Sully'' Sullivan, Carlo Angiuli, and Nathaniel Filardo double-checked the proof and provided valuable feedback on notation style and the flow of explanation.
Thanks as well to the anonymous OOPSLA reviewer \#4, whose suggestions helped improve the formality of our definitions.

This work was supported in part by
the member companies of the PDL Consortium (Broadcom,
Citadel, EMC, Facebook, Google, Hewlett-Packard Labs, Hitachi, Intel,
Microsoft Research, MongoDB, NetApp, Oracle, Samsung America, Seagate,
Tintri, Two Sigma, Uber, Veritas and Western Digital)
and by the U.S. Army Research Office under grant number W911NF0910273.
